---
title: "Raster Plot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Code for making raster plot of the button presses for Story Segmentation
Author: Cameron Perrin, cperrin@wustl.edu


### Plot one participant for one story

```{r, echo=FALSE,eval=TRUE, message= FALSE}
##Code for making raster plot of the button presses for Story Segmentation
#Author: Cameron Perrin, cperrin@wustl.edu
if(!require("dplyr")) install.packages("dplyr"); library(dplyr)
if(!require("ggplot2")) install.packages("ggplot2"); library(ggplot2)
if(!require("tidyverse")) install.packages("tidyverse");library(tidyverse)
if(!require("patchwork")) install.packages("patchwork");library(patchwork)

#load data
messy_data = read.csv("C:/Users/CKPer/Box/WashU/Peelle Lab/Story Segmentation/Online Sona data/gorilla data_long version/data_exp_15568-v3_task-j2vq.csv")
#want data for reaction time, for the space presses
messy_data = filter(messy_data, Response=="space")
reaction_time = select(messy_data, Participant.Private.ID, narrativeName, noiseCondition, Reaction.Time) #reaction time should be in ms, from the start of the story
#get rid of lecture practice data
reaction_time = filter(reaction_time, narrativeName!="Lecture1")

#try plotting pt 1268616 for Narrative 3
pt_1268618_N3 = filter(reaction_time, narrativeName=="Narrative3" & Participant.Private.ID=="1268616")
x0 = vector()
y0 = rep(0, nrow(pt_1268618_N3))
y1 = rep(1, nrow(pt_1268618_N3))
for(rt in pt_1268618_N3$Reaction.Time){
  x0 = c(x0, rt)
}
x0 = as.numeric(x0)
x0 = x0/1000 #convert to seconds from ms

plot(c(0, x0[length(x0)]), c(0,1), col = "white", xlab = "Time (seconds)", ylab = "", main = "Button Presses for pt 1268616, Narrative 3", axes=FALSE)
Axis(side=1, labels=TRUE)
segments(x0=x0, y0=y0, y1=y1)

```

### Plot multiple participants for one story, with corresponding histogram

```{r, echo=FALSE,eval=TRUE, message= FALSE}
#plot for Narrative 3, in quiet
n3_quiet_long = filter(reaction_time, narrativeName=="Narrative3" & noiseCondition=="quiet")
n3_quiet_long$Reaction.Time = as.numeric(n3_quiet_long$Reaction.Time)/1000
n3_quiet = pivot_wider(select(n3_quiet_long, -noiseCondition), names_from = narrativeName, values_from = Reaction.Time, values_fn = list(Reaction.Time = list))
library(plyr)
n3_quiet = rename(n3_quiet, c("Narrative3"="reaction_time"))

#n3_quiet = filter(n3_quiet, Participant.Private.ID!="1272888", Participant.Private.ID!="1301644", Participant.Private.ID!="1307287", Participant.Private.ID!="1310673", Participant.Private.ID!="1311497", Participant.Private.ID!="1273786", Participant.Private.ID!="1307732") #this removes all pt with only one response

#now plot on one big thing
ln_n3 = 228 #length of narrative 3 is 228 seconds - was using for x axis, but going to 250 looks better
plot(c(0, 250), c(0,nrow(n3_quiet)), col = "white", xlab = "Time (seconds)", ylab = "", main = "Button Presses for all pt for Narrative 3 in quiet", axes=FALSE)
Axis(side=1, labels=TRUE)
for(row in 1:nrow(n3_quiet)){
  y0 = rep(row-1, length(n3_quiet$reaction_time[row]))
  y1 = rep(row, length(n3_quiet$reaction_time[row]))
  #print(row)
  segments(x0=unlist(n3_quiet$reaction_time[row]), y0=y0, y1=y1) 
}


#add pt ids as y-axis labels? lots of effort maybe not worth it
#look into weird pt

#add histogram below it
hist(n3_quiet_long$Reaction.Time, main="", xlab="Time (seconds)", xlim=c(0,250), breaks=25)

```

Note: histogram includes the odd participant, so likely those spikes are from that participant

Look at that weird participant

```{r, echo=FALSE,eval=TRUE, message= FALSE}
#long = pivot_wider(select(n3_quiet_long, -noiseCondition), names_from = narrativeName, values_from = Reaction.Time, values_fn = list(Reaction.Time = length))

#pt 1301657
#try plotting pt for Narrative 3
pt_1301657_N3 = filter(reaction_time, narrativeName=="Narrative3" & Participant.Private.ID=="1301657")
x0 = vector()
y0 = rep(0, nrow(pt_1301657_N3))
y1 = rep(1, nrow(pt_1301657_N3))
for(rt in pt_1301657_N3$Reaction.Time){
  x0 = c(x0, rt)
}
x0 = as.numeric(x0)
x0 = x0/1000 #convert to seconds from ms

plot(c(0, x0[length(x0)]), c(0,1), col = "white", xlab = "Time (seconds)", ylab = "", main = "Button Presses for pt 1301657, Narrative 3", axes=FALSE)
Axis(side=1, labels=TRUE)
segments(x0=x0, y0=y0, y1=y1)

```

histogram without odd participant

```{r, echo=FALSE,eval=TRUE, message= FALSE}
n3_quiet_no_outlier = filter(n3_quiet_long, n3_quiet_long$Participant.Private.ID!="1301657")

hist(n3_quiet_no_outlier$Reaction.Time, main="", xlab="Time (seconds)", xlim=c(0,250), breaks=25)
```

